\sysfull

### 2018-04-16 paper/hwswsetup.tex
methodology: toolchain version
todos removed from methodology

We used two platforms to evaluate \sys: (1) an \emph{intermittently-powered}
energy-harvesting device, and (2) a \emph{continuously-powered} evaluation
board.
%
Every benchmark listed in the next section was run repeatedly on
each platform for a more or less long time window, depending on the benchmark,
to capture a diverse power trace and produce a high number of complete runs of all applications.
The results were averaged across the duration of the experiment.

Experiments on the intermittently-powered platform used the
WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator~\cite{} \todo{Add reference
to signal generator}{Przemek} emitting  a 20-\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table, so that the
WISP was parallel to the table surface at a height of 10~cm.
%
For distance-controlled experiments we positioned the signal generator
antenna at a fixed distance from the WISP. The distances were $d=\{15, 30,
50\}$\,cm for the main experiments and 60~cm for the task downscaling
experiments.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal.

@@

We evaluated \sys using six benchmarks summarized in
Table~\ref{table:benchmark_table}. %
Three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) are from prior
work~\cite{chain,alpaca} and three benchmarks (\textbf{dijkstra},
\textbf{fft}, \textbf{sort}) are new implementations of applications
from the MiBench suite~\cite{mibench,hicks_mibench2_2016}. The
\textbf{fft} implementation is based on the Accelerated FFT library from
TI~\cite{ti-fft}.
%
\todo{add reference}{Przemek}
%
All applications were compiled using MSP430 GCC~\cite{ti-gcc} version 6.4.0 with
\texttt{-O1} as optimization flag.
%
The source code for all benchmarks will be released at \cite{coala_website}.

@@

Manual instrumentation of Alpaca code is not a general approach, but only
served as a practical alternative to porting the compiler pass from LLVM to
GCC.
%
Our experiments show that manually-instrumented Alpaca code compiled with GCC
is about 30\%-40\% faster than Alpaca code instrumented automatically by the
Alpaca LLVM compiler pass and compiled with LLVM.
%
\todo{Provide concrete numbers for all applications}{Amjad}
%
This performance difference is due to the early experimental state of the
MSP430 backend for LLVM.
%
By compiling both systems with the same compiler (GCC), we ensure that our
comparison in Section~\ref{sec:evaluation} is fair.

>>>>

We used two platforms to evaluate \sys: (i) an \emph{intermittently-powered}
energy-harvesting device, and (i) a \emph{continuously-powered} evaluation
board.
%
Every benchmark listed in the next section was run repeatedly on
each platform for a more or less long time window, depending on the benchmark,
to capture a diverse power trace and produce a high number of complete runs of all applications.
The results were averaged across the duration of the experiment.

Experiments on the intermittently-powered platform used the
WISP\,5.1~\cite{wisp5,wisp} RF-powered energy-harvesting device.
%
The WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered the WISP using an RF signal generator emitting  a 20-\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with the WISP antenna, and
no objects obstructed the path.
%
We affixed the WISP with a paper harness at the edge of a table, so that the
WISP was parallel to the table surface at a height of 10\,cm.
%
For distance-controlled experiments we positioned the signal generator
antenna at a fixed distance from the WISP. The distances were $d=\{15, 30,
50\}$\,cm for the main experiments and 60\,cm for the task downscaling
experiments.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
the interval between edges in the signal.

@@

We evaluated \sys using six benchmarks summarized in
Table~\ref{table:benchmark_table}. %
Three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) are from prior
work~\cite{chain,alpaca} and three benchmarks (\textbf{dijkstra},
\textbf{fft}, \textbf{sort}) are new implementations of applications
from the MiBench suite~\cite{mibench,hicks_mibench2_2016}. The
\textbf{fft} implementation is based on the Accelerated FFT library from
TI~\cite{ti-fft}.
%
\todo{add reference}{Przemek}
%
All applications were compiled using MSP430 GCC~\cite{ti-gcc} version 6.4.0
from toolchain version 5.01.01.00 with \texttt{-O1} as optimization flag.
%
The source code for all benchmarks will be released at \cite{coala_website}.

@@

Manual instrumentation of Alpaca code is not a general approach, but only
served as a practical alternative to porting the compiler pass from LLVM to
GCC.
%
Our experiments show that manually-instrumented Alpaca code compiled with GCC
is about 30\%-40\% faster than Alpaca code instrumented automatically by the
Alpaca LLVM compiler pass and compiled with LLVM. This performance difference is due to the early experimental state of the MSP430 backend for LLVM.
%
By compiling both systems with the same compiler (GCC), we ensure that our
comparison in Section~\ref{sec:evaluation} is fair.
